\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-11 doc/flexiblesusy-paper.tex
adding table with unit tested (N)MSSM parameter points
I also added a note about the tests of the EWSB iterations.
Update description of MSSMD5O + MSSMRHN tower in paper

\subsubsection{Extending existing models}

The preceding example was a modest alteration of a physics scenario
in that an existing model has been reused.
A more non-trivial modification might involve
an extension of the particle content as well as the interactions.
One of the simplest classes of models beyond the MSSM is
those with additional gauge-singlet fields.
In what follows, a supersymmetric type-I see-saw model
\cite{see-saw} 
shall be considered in which
three neutral (heavy) chiral superfields are introduced.

% To create a new model, one should name it.
In the package, this model is named \code{MSSMRHN}, standing for
the MSSM plus right-handed neutrinos.
% Since \fs needs the outcome of \sarah,
One needs to prepare an input file to \sarah which might be placed in
\code{<FlexibleSUSY-root>/sarah/MSSMRHN/} or
\code{<SARAH-root>/Models/MSSMRHN/}.
The input file \code{MSSMRHN.m} contains
the declaration of the three-generation singlets \code{v}:
\begin{numlstlisting}[name=MSSMRHN.m]
SuperFields[[8]] = {v, 3, conj[vR], 0, 1, 1, RpM};
\end{numlstlisting}
as well as the neutrino Yukawa couplings and the Majorana mass terms
of the singlets:
\begin{numlstlisting}[name=MSSMRHN.m]
SuperPotential = Yu u.q.Hu - Yd d.q.Hd - Ye e.l.Hd + \[Mu] Hu.Hd +
                 Yv v.l.Hu + Mv/2 v.v;
\end{numlstlisting}
Further declarations inform \sarah
of how to form Dirac spinors out of the new Weyl spinors
and how the scalars and the fermions mix to comprise
the mass eigenstates:
\begin{numlstlisting}[name=MSSMRHN.m]
DEFINITION[GaugeES][DiracSpinors] = {
  Fu1 -> {FuL, 0}, Fu2 -> {0, FuR},
  Fv1 -> {FvL, 0}, Fv2 -> {0, FvR},
  ...
};

@@

Finally, it remains to put \code{FlexibleSUSY.m.in}
in \code{model_files/MSSMRHN/}.
The high-scale boundary conditions therein might read:
\begin{numlstlisting}
HighScaleInput = {
  {Mv, LHInput[Mv]}, {B[Mv], LHInput[B[Mv]]},
  {Yv, LHInput[Yv]}, {T[Yv], Azero*Yv},
  {mv2, UNITMATRIX[3] m0^2},
  ...
};
\end{numlstlisting}
In this particular example,
the new parameters shown in lines 2--3
are constrained at the $M_X$ scale
to the values given in the SLHA input file.
In a data-driven approach,
they might alternatively be fixed from a matching against
a low-energy theory containing the dimension-5
neutrino mass operator in conjunction with supplementary constraints.

With the above set of input files,
\fs can generate the C++ code and compile it
to produce \code{libMSSMRHN}.
These products shall be employed as the implementation of the theory that
underlies the MSSM in the next subsection.

@@

There are problems which one cannot solve only by
editing \mathematica model files.
To unlock the full potential of \fs,
it is an advantage not to avoid programming at the C++ level.
For this, it should help to have working knowledge about the basic structure
of a spectrum generator, set out in \secref{sec:SpecGenStruct}.
In what follows,
it shall be demonstrated that
the clean class structure serves as firm guidance on the job.

The procedure described above is essentially all that is needed
to employ new spectrum generator components,
which may be composed from scratch or through
a linkage to external routines.
In doing so,
notice that there was an evident limit on the scope of
modules which one had to deal with.
For instance, it was clear from the outset
that one does not have to go through the code of the central
fixed-point iteration engine, \code{RGFlow}.
This manifests the power of the clear separation among objects
each with its well-defined distinct role.
This is just like the fact that one does not need to access the internals
of the \code{std::sort} function in the C++ Standard Library.
It might be entertaining to complete the analogy by
mapping the model objects in \code{RGFlow}
to the elements that \code{std::sort} sorts
and the boundary condition objects
to the comparator function.

@@

@@

Consider a physics scenario which is best described
by a tower of effective theories.
Within the framework of \fs, the C++ class structure is
a faithful reflection of
this physicist's view on the given problem.
Here we illustrate this point
using a well-known configuration in which
the higher-energy theory is the MSSMRHN discussed above which
gives rise to the MSSM as the lower-energy effective theory.
The relevant classes are sketched
in \figref{fig:class structure for tower}.
\begin{figure}
  \centering
\begin{tikzpicture}
  \draw (0,-.5) coordinate(bottom)
        (0,-.4)
     -- (0,0)  coordinate(MZ) node[left] {$M_Z$}
     -- (0,.7) coordinate(MS) node[left] {$M_S$}
     -- (0,2)  coordinate(Mv) node[left] {$M_\nu$}
     -- (0,3)  coordinate(MX) node[left] {$M_X$}
     -- (0,3.4)
        (0,3.5) coordinate(top);

@@

  \draw (MZ) +(-.1,0) -- +(+.1,0); \draw[<-] (MZ) ++(-.8,0) -- ++(-.5,0)
     node[left,draw] {\code{MSSM_low_scale_constraint}};
  \draw (MS) +(-.1,0) -- +(+.1,0); \draw[<-] (MS) ++(-.8,0) -- ++(-.5,0)
     node[left,draw] {\code{MSSM_susy_scale_constraint}};
  \draw (Mv) +(-.1,0) -- +(+.1,0); \draw[<-] (Mv) ++(-.8,0) -- ++(-.5,0)
     node[left,draw] {\code{MSSM_MSSMRHN_matching}};
  \draw (MX) +(-.1,0) -- +(+.1,0); \draw[<-] (MX) ++(-.8,0) -- ++(-.5,0)
     node[left,draw] {\code{MSSMRHN_high_scale_constraint}};

  \draw (MvRR) +(0,-.03) rectangle (MZR) node[pos=.5] {\code{MSSM}};
  \draw (MvRR) +(0, .03) rectangle (MXR) node[pos=.5] {\code{MSSMRHN}};

  \path (bottom) +(3.8,0) coordinate(SE) (top) +(-6.8,0) coordinate(NW);
  \draw  (NW) +(0,.5) rectangle (SE)
         (NW) -- +(10.6,0);
  \path (top) node[above] {\code{RGFlow}};
\end{tikzpicture}
  \caption{Schematic class structure in the C++ code for
    the tower scenario.}
  \label{fig:class structure for tower}
\end{figure}
The \code{MSSMRHN} object is in effect from the $M_X$ scale down to
the $M_\nu$ scale at which the right-handed neutrinos are decoupled.
Below this scale, the \code{MSSM} object takes over.
On the left of the vertical axis,
the boundary condition objects acting on either model are displayed,
together with the matching object connecting the two theories.
Note that each of the boundary condition and matching objects
maintains and updates its own scale over iterations.
An arrow in the figure depicts
the association of a constraint with its scale.
All these components are plugged into the \code{RGFlow} object
which then solves the problem.

@@

As the target spectrum generator depends on two models,
one should first build these prerequisites by:
\begin{numlstlisting}
$ ./createmodel --name=MSSM
$ ./createmodel --name=MSSMRHN
$ ./configure --with-models=MSSM,MSSMRHN
$ make
\end{numlstlisting}
As a by-product, line 3
also creates a \code{Makefile} in \code{examples/tower/}.
One can best see the overall code structure of the application in this file:
\begin{numlstlisting}
CPPFLAGS  := -I. $(INCCONFIG) $(INCFLEXI) $(INCLEGACY) $(INCSLHAEA) \
             $(INCMSSM) $(INCMSSMRHN)

TOWER_SRC := run_tower.cpp \
	     MSSM_MSSMRHN_two_scale_matching.cpp \
	     MSSM_MSSMRHN_two_scale_initial_guesser.cpp

@@

run_tower.x: $(TOWER_OBJ) $(LIBMSSM) $(LIBMSSMRHN) $(LIBFLEXI) $(LIBLEGACY)
  $(CXX) -o $@ $^ $(LOOPFUNCLIBS) $(GSLLIBS) $(BOOSTTHREADLIBS) $(THREADLIBS) $(LAPACKLIBS) $(FLIBS)
\end{numlstlisting}
The include directives in line 2 tell the compiler
where to find the headers for either \code{MSSM} or \code{MSSMRHN}.
The \code{.cpp} files in lines 4--6 and the \code{.hpp} files
that they include are to be written by hand.
Obviously, the executable \code{run_tower.x}, in line 10, depends on both
\code{$(LIBMSSM)} and \code{$(LIBMSSMRHN)}
that implement the auto-generated
components in \figref{fig:class structure for tower}.

To prepare the main source file \code{run_tower.cpp},
one can extend % make a straightforward extension to
\code{run_MSSM.cpp} or \code{run_MSSMRHN.cpp}
produced in either model directory.
The shipped example reads:
\begin{numlstlisting}
#include "MSSM_MSSMRHN_spectrum_generator.hpp"

int main(int argc, char* argv[])
{
  // define objects;
  QedQcd oneset;
  MSSM_input_parameters    input_1;
  MSSMRHN_input_parameters input_2;
  // fill in input_1 and input_2;
  oneset.toMz(); // run SM fermion masses to MZ
  typedef Two_scale algorithm_type;
  MSSM_MSSMRHN_spectrum_generator<algorithm_type> spectrum_generator;
  // set up spectrum_generator;
  spectrum_generator.run(oneset, input_1, input_2);
  // extract outcome from models;
}
\end{numlstlisting}
where a line in the form \code{// ...;} shall be understood
to be a pseudo-code.
Given two models,
one declares two sets of input parameters,
\code{input_1} and \code{input_2}, in lines 7--8.

@@

\code{MSSM_MSSMRHN_spectrum_generator} object in line 12, which

@@

\code{MSSM_MSSMRHN_spectrum_generator.hpp} and reads:

@@

template<class T> void MSSM_MSSMRHN_spectrum_generator<T>::run

@@

 const MSSM_input_parameters& input_1, const MSSMRHN_input_parameters& input_2)

@@

  susy_scale_constraint_1.clear(); // of type MSSM_susy_scale_constraint<T>
  low_scale_constraint_1 .clear(); // of type MSSM_low_scale_constraint<T>
  matching.reset();                // of type MSSM_MSSMRHN_matching<T>

@@

  matching.set_upper_input_parameters(input_2);

@@

the corresponding part of \code{MSSM_spectrum_generator.hpp}.

@@

the constraints on \code{MSSM}:

@@

and initializes the \code{MSSM} object:

@@

  model_1.clear();                 // of type MSSM<T>

@@

\code{MSSM_convergence_tester} and \code{MSSMRHN_convergence_tester}:

@@

  MSSM_convergence_tester<T> convergence_tester_1(&model_1, precision_goal);

@@

  MSSM_MSSMRHN_initial_guesser<T> initial_guesser
    (&model_1, &model_2, input_2, oneset,

@@

  model_1.run_to(susy_scale_1);    // of type MSSM<T>

@@

One needs to write the matching class for a particular pair of
models from scratch.
It shall be based on the abstract class \code{Matching<Two_scale>}
that comes with \fs.
In the present example, the class is declared in the header
\code{MSSM_MSSMRHN_two_scale_matching.hpp}:
\begin{numlstlisting}
template<> class MSSM_MSSMRHN_matching<Two_scale> : public Matching<Two_scale> {
public:
  MSSM_MSSMRHN_matching();
  MSSM_MSSMRHN_matching(const MSSMRHN_input_parameters&);
  void match_low_to_high_scale_model();
  void match_high_to_low_scale_model();
  double get_scale() const;
  void set_models(Two_scale_model *lower, Two_scale_model *upper);
  double get_initial_scale_guess() const;
  void set_upper_input_parameters(const MSSMRHN_input_parameters&);
  void set_scale(double);
  void reset();
private:
  MSSM   <Two_scale> *lower;
  MSSMRHN<Two_scale> *upper;
  void make_initial_scale_guess();
  void update_scale();
  ...
};
\end{numlstlisting}
As lines 4 and 10 indicate,
this class takes an \code{MSSMRHN_input_parameters} object as input.
The \code{MvInput} field thereof is referenced
for the initial guess of the matching scale
in line 25 of \code{MSSM_MSSMRHN_two_scale_matching.cpp}:
\begin{numlstlisting}
void MSSM_MSSMRHN_matching<Two_scale>::match_low_to_high_scale_model()
{
  upper->set_Yd(lower->get_Yd());
  // copy rest of couplings from lower to upper;
  upper->set_scale(lower->get_scale());
}

void MSSM_MSSMRHN_matching<Two_scale>::match_high_to_low_scale_model()
{
  update_scale();
  lower->set_Yd(upper->get_Yd());
  // copy rest of couplings from upper to lower;
  lower->set_scale(upper->get_scale());
}

void MSSM_MSSMRHN_matching<Two_scale>::set_upper_input_parameters
(const MSSMRHN_input_parameters& inputPars_)
{
  inputPars = inputPars_;
  make_initial_scale_guess();
}

void MSSM_MSSMRHN_matching<Two_scale>::make_initial_scale_guess()
{
  double RHN_scale = pow(abs(inputPars.MvInput.determinant()), 1.0/3);
  scale = initial_scale_guess = RHN_scale;
}

void MSSM_MSSMRHN_matching<Two_scale>::update_scale()
{
  double RHN_scale = pow(abs(upper->get_Mv().determinant()), 1.0/3);
  scale = RHN_scale;
}
\end{numlstlisting}
Recall that \code{MvInput} is the high-scale boundary value of \code{Mv}.
If one had opted for an alternative strategy to fix \code{Mv},
then \code{MSSM_MSSMRHN_matching} might have required a different input.
Subsequently, the matching scale is updated at each iteration
to be the geometric mean of the running \code{Mv} eigenvalues
in lines 31--32.
The actual matching process takes place in the two functions
\code{match_low_to_high_scale_model} and \code{match_high_to_low_scale_model}.
For brevity,
their examples shown above simply copy each coupling
upwards or downwards, neglecting threshold corrections.
The way to incorporate these corrections should be self-evident
from the code structure.

% \begin{numlstlisting}
% template<>
% class MSSM_MSSMRHN_initial_guesser<Two_scale> : public Initial_guesser<Two_scale> {
% public:
%   MSSM_MSSMRHN_initial_guesser(MSSM<Two_scale>*, MSSMRHN<Two_scale>*,
%                                const MSSMRHN_input_parameters&,
%                                const QedQcd&,
%                                const MSSM_low_scale_constraint<Two_scale>&,
%                                const MSSM_susy_scale_constraint<Two_scale>&,
%                                const MSSMRHN_high_scale_constraint<Two_scale>&,
%                                const MSSM_MSSMRHN_matching<Two_scale>&);
%   virtual ~MSSM_MSSMRHN_initial_guesser();
%   virtual void guess();
%
% private:
%   MSSM   <Two_scale>* model_1;
%   MSSMRHN<Two_scale>* model_2;
%   MSSMRHN_input_parameters input_pars;
%   QedQcd oneset;
%   MSSM_low_scale_constraint<Two_scale> low_constraint;
%   MSSM_susy_scale_constraint<Two_scale> susy_constraint;
%   MSSMRHN_high_scale_constraint<Two_scale> high_constraint;
%   MSSM_MSSMRHN_matching<Two_scale> matching;
% };
% \end{numlstlisting}
The last missing piece is the initial guesser.
One can extend the already available
\code{MSSM_initial_guesser} class. % in a straightforward manner.
The essential task is done by the following member function:
\begin{numlstlisting}[name=MSSM_MSSMRHN_two_scale_initial_guesser.cpp]
void MSSM_MSSMRHN_initial_guesser<Two_scale>::guess()
{
  // guess SUSY couplings in model-1 at low energy;

>>>>

\subsubsection{Extending existing models}
\label{sec:extending existing models}

The preceding example was a modest alteration of a physics scenario
in that an existing model has been reused.
A more non-trivial modification might involve
an extension of the particle content as well as the interactions.
One of the simplest classes of models beyond the MSSM is
those with additional gauge-singlet fields.
In what follows, a supersymmetric type-I see-saw scenario
\cite{see-saw} 
shall be considered.
For this, two extensions of the MSSM are introduced:
MSSMRHN with three extra neutral (heavy) chiral superfields,
and MSSMD5O with the dimension-5 neutrino mass operator
added to the superpotential.
Both models are included in the package.

% To create a new model, one should name it.
The name MSSMRHN of the first model stands for
the MSSM plus right-handed neutrinos.
% Since \fs needs the outcome of \sarah,
One needs to prepare an input file to \sarah which might be placed in
\code{<FlexibleSUSY-root>/sarah/MSSMRHN/} or
\code{<SARAH-root>/Models/MSSMRHN/}.
The input file \code{MSSMRHN.m} contains
the declaration of the three-generation singlets \code{v}:
\begin{numlstlisting}[name=MSSMRHN.m]
SuperFields[[8]] = {v, 3, conj[vR], 0, 1, 1, RpM};
\end{numlstlisting}
as well as the neutrino Yukawa couplings and the Majorana mass terms
of the singlets:
\begin{numlstlisting}[name=MSSMRHN.m]
SuperPotential = Yu u.q.Hu - Yd d.q.Hd - Ye e.l.Hd + \[Mu] Hu.Hd +
                 Yv v.l.Hu + Mv/2 v.v;
\end{numlstlisting}
Further declarations inform \sarah
of how to form Dirac spinors out of the new Weyl spinors
and how the scalars and the fermions mix to comprise
the mass eigenstates:
\begin{numlstlisting}[name=MSSMRHN.m]
DEFINITION[GaugeES][DiracSpinors] = {
  Fu1 -> {FuL, 0}, Fu2 -> {0, FuR},
  Fv1 -> {FvL, 0}, Fv2 -> {0, FvR},
  ...
};

@@

Finally, it remains to put \code{FlexibleSUSY.m.in}
in \code{model_files/MSSMRHN/}.
The high-scale boundary conditions therein might read:
\begin{numlstlisting}
HighScaleInput = {
  {mv2, UNITMATRIX[3] m0^2},
  {T[Yv], Azero*Yv},
  {B[Mv], LHInput[B[Mv]]},
  ...
};
\end{numlstlisting}

The second model is called MSSMD5O, standing for
the MSSM including the dimension-5 operator.
Obviously, one can compose it by adding
the additional term to the superpotential in \code{MSSMD5O.m}:
\begin{numlstlisting}
SuperPotential = Yu u.q.Hu - Yd d.q.Hd - Ye e.l.Hd + \[Mu] Hu.Hd \
               + WOp/2 l.Hu.l.Hu;
\end{numlstlisting}
where line 2 contains the dimension-5 operator
multiplied by its coeffficient matrix \code{WOp}.
The declarations of the neutrino Dirac spinors and mixing are
very similar to those in the MSSMRHN,
except that \code{FvR} is absent.

One can specify the low-scale constraints on \code{WOp}
in \code{model_files/MSSMRHN/FlexibleSUSY.m.in}:
\begin{numlstlisting}
EXTPAR = {
  {1, mv1}, {2, mv2}, {3, mv3},
  {4, ThetaV12}, {5, ThetaV13}, {6, ThetaV23},
  {7, YvDiag1}, {8, YvDiag2}, {9, YvDiag3}
};

UPMNS = Module[{
    s12 = Sin @ ThetaV12, c12 = Cos @ ThetaV12,
    s13 = Sin @ ThetaV13, c13 = Cos @ ThetaV13,
    s23 = Sin @ ThetaV23, c23 = Cos @ ThetaV23
  },
  {{  c12 c13              ,  s12 c13              , s13     },
   { -s12 c23 - c12 s23 s13,  c12 c23 - s12 s23 s13, s23 c13 },
   {  s12 s23 - c12 c23 s13, -c12 s23 - s12 c23 s13, c23 c13 }}
];

mv = conj[UPMNS].DiagonalMatrix[{mv1, mv2, mv3}].Transpose[conj @ UPMNS];

LowScaleInput = Join[
  { (* MSSM low-scale constraints *) },
  Flatten[Table[{WOp[i,j], mv[[i,j]] / (vu/Sqrt[2])^2}, {i,3}, {j,3}], 1]
];

InitialGuessAtLowScale = Join[
  { (* MSSM initial guesses at low scale *) },
  Flatten[Table[{WOp[i,j], mv[[i,j]] / (vu/Sqrt[2])^2}, {i,3}, {j,3}], 1]
];
\end{numlstlisting}
The \code{EXTPAR} list contains the input parameters
to be read from the corresponding SLHA block.
The low-energy neutrino mass eigenvalues and mixing angles are
declared in lines 2--3.
They are followed by the neutrino Yukawa eigenvalues,
which shall be used as part of the matching condition
described in \ref{sec:tower construction}.
The constraint on and the initial guess of \code{WOp}
in lines 21 and 26 should be self-explanatory.

With the above set of input files,
\fs can generate the C++ class libraries,
\code{libMSSMRHN} and \code{libMSSMD5O}\@.
These products shall be employed as the two effective theories
in the implementation of the see-saw mechanism.
To this end, one further needs to code at the C++ level,
as explained in the next subsection and \ref{sec:tower construction}.

@@

There are problems which one cannot solve only by
editing \mathematica model files.
To unlock the full potential of \fs,
it is an advantage not to avoid programming at the C++ level.
For this, it should help to have working knowledge about the basic structure
of a spectrum generator, set out in \secref{sec:SpecGenStruct}.
In \ref{sec:examples of c++ code adaptation},
two examples are presented for demonstrating that
the clean class structure serves as firm guidance on the job.

The first project in \ref{sec:tower construction} is
to build a spectrum generator that can handle
a tower of multiple effective field theories.
The aim is to take a first step towards
a study of slepton-mediated lepton flavour violation
due to radiative corrections in the type-I supersymmetric see-saw model
\cite{Borzumati:1986qx}.
To this end, \code{MSSMRHN} is stacked on top of \code{MSSMD5O}.
The preparation of these two models has been covered in
\secref{sec:extending existing models}.

The spectrum generator shall accept
the low-energy neutrino masses and mixing angles
which determine \code{WOp}, the coefficients
of the $L H_u L H_u$ operator.
These $6 \times 6$ coefficients evolve to
the right-handed neutrino mass scale at which
they are matched to the neutrino Yukawa couplings \code{Yv} and
the right-handed neutrino masses \code{Mv}.
Since there are more degrees of freedom in the pair of
\code{Yv} and \code{Mv} than in \code{WOp},
one needs supplementary conditions in addition to the see-saw relation.
In the presented matching code, it is assumed that all mixing in \code{WOp}
stems from the left-handed rotation of \code{Yv} whose eigenvalues are
fixed to those specified by the user.
The non-trivial flavour structure of the neutrino Yukawa couplings then
causes running slepton mass matrices to acquire flavour-violating elements.
The output from the spectrum generator includes
the slepton mass matrices as well as
the resulting mass eigenvalues and mixing.
One might pass this outcome on to another routine
to calculate rates of lepton flavour violating processes.

For brevity,
threshold corrections are ignored
in the specimen matching code connecting the two models
as well as in the low-scale boundary condition on \code{WOp}
from the neutrino oscillation data.
Therefore, the result maintains only the accuracy of one-loop RGEs,
even though two-loop $\beta$-functions are computed by each model class.
For a full accuracy of two-loop RGEs, one can incorporate the omitted
one-loop corrections into the constraint classes.
The way to implement them should be self-evident from the code structure.

The second project in \ref{sec:integrating-custom-built} shows
% is essentially all that is needed
how one can employ new spectrum generator components,
which may be composed from scratch or through
a linkage to external routines.
In the procedure,
it would be noticed that there is an evident limit on the scope of
modules which one has to deal with.
For instance, it is clear from the outset
that one does not have to go through the code of the central
fixed-point iteration engine, \code{RGFlow}.
This manifests the power of the clear separation among objects
each with its well-defined distinct role.
This is just like the fact that one does not need to access the internals
of the \code{std::sort} function in the C++ Standard Library.
It might be entertaining to complete the analogy by
mapping the model objects in \code{RGFlow}
to the elements that \code{std::sort} sorts
and the boundary condition objects
to the comparator function.

@@

In what follows, technical details of \fs programming at the C++ level are
set out which supplement the outline given
in \secref{sec:adapting-cpp-code}.

@@

Consider a physics scenario which is best described
by a tower of effective theories.
Within the framework of \fs, the C++ class structure is
a faithful reflection of
this physicist's view on the given problem.
Here we illustrate this point
using a well-known configuration in which
the higher-energy theory is the MSSMRHN which
gives rise to the MSSMD5O as the lower-energy effective theory.
The relevant classes are sketched
in \figref{fig:class structure for tower}.
\begin{figure}
  \centering
\begin{tikzpicture}
  \draw (0,-.5) coordinate(bottom)
        (0,-.4)
     -- (0,0)  coordinate(MZ) node[left] {$M_Z$}
     -- (0,.7) coordinate(MS) node[left] {$M_S$}
     -- (0,2)  coordinate(Mv) node[left] {$M_\nu$}
     -- (0,3)  coordinate(MX) node[left] {$M_X$}
     -- (0,3.4)
        (0,3.5) coordinate(top);

@@

  \draw (MZ) +(-.1,0) -- +(+.1,0); \draw[<-] (MZ) ++(-.8,0) -- ++(-.5,0)
     node[left,draw] {\code{MSSMD5O_low_scale_constraint}};
  \draw (MS) +(-.1,0) -- +(+.1,0); \draw[<-] (MS) ++(-.8,0) -- ++(-.5,0)
     node[left,draw] {\code{MSSMD5O_susy_scale_constraint}};
  \draw (Mv) +(-.1,0) -- +(+.1,0); \draw[<-] (Mv) ++(-.8,0) -- ++(-.5,0)
     node[left,draw] {\code{MSSMD5O_MSSMRHN_matching}};
  \draw (MX) +(-.1,0) -- +(+.1,0); \draw[<-] (MX) ++(-.8,0) -- ++(-.5,0)
     node[left,draw] {\code{MSSMRHN_high_scale_constraint}};

  \draw (MvRR) +(0,-.03) rectangle (MZR) node[pos=.5] {\code{MSSMD5O}};
  \draw (MvRR) +(0, .03) rectangle (MXR) node[pos=.5] {\code{MSSMRHN}};

  \path (bottom) +(3.8,0) coordinate(SE) (top) +(-6.8,0) coordinate(NW);
  \draw  (NW) +(0,.5) rectangle (SE)
         (NW) -- +(10.6,0);
  \path (top) node[above] {\code{RGFlow}};
\end{tikzpicture}
  \caption{Schematic class structure in the C++ code for
    the tower scenario.}
  \label{fig:class structure for tower}
\end{figure}
The \code{MSSMRHN} object is in effect from the $M_X$ scale down to
the $M_\nu$ scale at which the right-handed neutrinos are decoupled.
Below this scale, the \code{MSSMD5O} object takes over.
On the left of the vertical axis,
the boundary condition objects acting on either model are displayed,
together with the matching object connecting the two theories.
Note that each of the boundary condition and matching objects
maintains and updates its own scale over iterations.
An arrow in the figure depicts
the association of a constraint with its scale.
All these components are plugged into the \code{RGFlow} object
which then solves the problem.

@@

As the target spectrum generator depends on two models,
one should first build these prerequisites by:
\begin{numlstlisting}
$ ./createmodel --name=MSSMD5O
$ ./createmodel --name=MSSMRHN
$ ./configure --with-models=MSSMD5O,MSSMRHN
$ make
\end{numlstlisting}
As a by-product, line 3
also creates a \code{Makefile} in \code{examples/tower/}.
One can best see the overall code structure of the application in this file:
\begin{numlstlisting}
CPPFLAGS  := -I. $(INCCONFIG) $(INCFLEXI) $(INCLEGACY) $(INCSLHAEA) \
             $(INCMSSMD5O) $(INCMSSMRHN)

TOWER_SRC := run_tower.cpp \
	     MSSMD5O_MSSMRHN_two_scale_matching.cpp \
	     MSSMD5O_MSSMRHN_two_scale_initial_guesser.cpp

@@

run_tower.x: $(TOWER_OBJ) $(LIBMSSMD5O) $(LIBMSSMRHN) $(LIBFLEXI) $(LIBLEGACY)
  $(CXX) -o $@ $^ $(LOOPFUNCLIBS) $(GSLLIBS) $(BOOSTTHREADLIBS) $(THREADLIBS) $(LAPACKLIBS) $(BLASLIBS) $(FLIBS)
\end{numlstlisting}%% $
The include directives in line 2 tell the compiler
where to find the headers for either \code{MSSMD5O} or \code{MSSMRHN}.
The \code{.cpp} files in lines 4--6 and the \code{.hpp} files
that they include are to be written by hand.
Obviously, the executable \code{run_tower.x}, in line 10, depends on both
\code{$(LIBMSSMD5O)} and \code{$(LIBMSSMRHN)}
that implement the auto-generated
components in \figref{fig:class structure for tower}.

To prepare the main source file \code{run_tower.cpp},
one can extend % make a straightforward extension to
\code{run_MSSMD5O.cpp} or \code{run_MSSMRHN.cpp}
produced in either model directory.
The shipped example reads:
\begin{numlstlisting}
#include "MSSMD5O_MSSMRHN_spectrum_generator.hpp"

int main(int argc, char* argv[])
{
  // define objects;
  QedQcd oneset;
  MSSMD5O_input_parameters input_1;
  MSSMRHN_input_parameters input_2;
  // fill in input_1 and input_2;
  oneset.toMz(); // run SM fermion masses to MZ
  typedef Two_scale algorithm_type;
  MSSMD5O_MSSMRHN_spectrum_generator<algorithm_type> spectrum_generator;
  // set up spectrum_generator;
  spectrum_generator.run(oneset, input_1, input_2);
  // extract outcome from models;
}
\end{numlstlisting}
where a line in the form \code{// ...;} shall be understood
to be a pseudo-code.
Given two models,
one declares two sets of input parameters,
\code{input_1} and \code{input_2}, in lines 7--8.

@@

\code{MSSMD5O_MSSMRHN_spectrum_generator} object in line 12, which

@@

\code{MSSMD5O_MSSMRHN_spectrum_generator.hpp} and reads:

@@

template<class T> void MSSMD5O_MSSMRHN_spectrum_generator<T>::run

@@

 const MSSMD5O_input_parameters& input_1, const MSSMRHN_input_parameters& input_2)

@@

  susy_scale_constraint_1.clear(); // of type MSSMD5O_susy_scale_constraint<T>
  low_scale_constraint_1 .clear(); // of type MSSMD5O_low_scale_constraint<T>
  matching.reset();                // of type MSSMD5O_MSSMRHN_matching<T>

@@

  matching.set_lower_input_parameters(input_1);

@@

the corresponding part of \code{MSSMD5O_spectrum_generator.hpp}.

@@

the constraints on \code{MSSMD5O}:

@@

and initializes the \code{MSSMD5O} object:

@@

  model_1.clear();                 // of type MSSMD5O<T>

@@

\code{MSSMD5O_convergence_tester} and \code{MSSMRHN_convergence_tester}:

@@

  MSSMD5O_convergence_tester<T> convergence_tester_1(&model_1, precision_goal);

@@

  MSSMD5O_MSSMRHN_initial_guesser<T> initial_guesser
    (&model_1, &model_2, input_1, oneset,

@@

  model_1.run_to(susy_scale_1);    // of type MSSMD5O<T>

@@

One needs to write the matching class for a particular pair of
models from scratch.
It shall be based on the abstract class \code{Matching<Two_scale>}
that comes with \fs.
In the present example, the class is declared in the header
\code{MSSMD5O_MSSMRHN_two_scale_matching.hpp}:
\begin{numlstlisting}
template<> class MSSMD5O_MSSMRHN_matching<Two_scale> : public Matching<Two_scale> {
public:
  MSSMD5O_MSSMRHN_matching();
  MSSMD5O_MSSMRHN_matching(const MSSMD5O_input_parameters&);
  void match_low_to_high_scale_model();
  void match_high_to_low_scale_model();
  double get_scale() const;
  void set_models(Two_scale_model *lower, Two_scale_model *upper);
  double get_initial_scale_guess() const;
  void set_lower_input_parameters(const MSSMD5O_input_parameters&);
  void set_scale(double);
  void reset();
private:
  MSSMD5O<Two_scale> *lower;
  MSSMRHN<Two_scale> *upper;
  void make_initial_scale_guess();
  void update_scale();
  ...
};
\end{numlstlisting}
As lines 4 and 10 indicate,
this class takes an \code{MSSMD5O_input_parameters} object as input.
The low-energy neutrino data therein is referenced by
\code{make_initial_scale_guess}
starting from line 23 of \code{MSSMD5O_MSSMRHN_two_scale_matching.cpp}:
\begin{numlstlisting}
void MSSMD5O_MSSMRHN_matching<Two_scale>::invert_seesaw_formula
(const Eigen::Matrix3d& WOp, const Eigen::Vector3d& YvDiag,
 Eigen::Matrix3d& Yv, Eigen::Matrix3d& Mv)
{
  Eigen::Matrix3cd uh;
  Eigen::Array3d s;
  fs_diagonalize_symmetric(WOp, s, uh);
  Eigen::Matrix3d U = uh.adjoint().real();
  Eigen::Vector3d YvDiagInv(1, 1, 1);
  YvDiagInv.array() /= YvDiag.array();
  Eigen::Matrix3d YvInv = U * YvDiagInv.asDiagonal();
  Mv = (YvInv.transpose() * WOp * YvInv).inverse();
  Yv = YvDiag.asDiagonal() * U.adjoint();
}

void MSSMD5O_MSSMRHN_matching<Two_scale>::set_lower_input_parameters
(const MSSMD5O_input_parameters& inputPars_)
{
  inputPars = inputPars_;
  make_initial_scale_guess();
}

void MSSMD5O_MSSMRHN_matching<Two_scale>::make_initial_scale_guess()
{
  Eigen::Matrix3d WOp;
  // fill WOp with elements in terms of data from inputPars;
  Eigen::Vector3d YvDiag;
  YvDiag << inputPars.YvDiag1, inputPars.YvDiag2, inputPars.YvDiag3;
  Eigen::Matrix3d Yv;
  Eigen::Matrix3d Mv;
  invert_seesaw_formula(WOp, YvDiag, Yv, Mv);
  double RHN_scale = pow(abs(Mv.determinant()), 1.0/3);
  scale = initial_scale_guess = RHN_scale;
}
\end{numlstlisting}
To guess the matching scale, this function estimates
the right-handed neutrino mass matrix \code{Mv}
from \code{WOp}, the dimension-5 operator coefficients,
and \code{YvDiag}, the neutrino Yukawa eigenvalues,
by calling \code{invert_seesaw_formula}.
Since the mapping,
$\mbox{\code{WOp}} \rightarrow (\mbox{\code{Yv}}, \mbox{\code{Mv}})$,
is not unique, \code{invert_seesaw_formula}
opts to impose the following additional constraints:
the eigenvalues of \code{Yv} are fixed to the user input (line 10),
and all mixing in \code{WOp} originates from the rotation of the SU(2)
doublets (line 11).

The actual matching process takes place in the two functions
\code{match_low_to_high_scale_model} and \code{match_high_to_low_scale_model}:
\begin{numlstlisting}
void MSSMD5O_MSSMRHN_matching<Two_scale>::match_low_to_high_scale_model()
{
  Eigen::Vector3d YvDiag;
  YvDiag << inputPars.YvDiag1, inputPars.YvDiag2, inputPars.YvDiag3;
  Eigen::Matrix3d Yv;
  Eigen::Matrix3d Mv;
  invert_seesaw_formula(lower->get_WOp(), YvDiag, Yv, Mv);
  upper->set_Yv(Yv);
  upper->set_Mv(Mv);

  upper->set_Yd(lower->get_Yd());
  // copy rest of couplings from lower to upper;
  upper->set_scale(lower->get_scale());
}

void MSSMD5O_MSSMRHN_matching<Two_scale>::match_high_to_low_scale_model()
{
  update_scale();

  const auto& Yv = upper->get_Yv();
  const auto& Mv = upper->get_Mv();
  lower->set_WOp(Yv.transpose() * Mv.inverse() * Yv);

  lower->set_Yd(upper->get_Yd());
  // copy rest of couplings from upper to lower;
  lower->set_scale(upper->get_scale());
}
